ABC Group Level Fits

### 2024-01-20 Model/abc_hier.qmd
minor

pacman::p_load(tidyverse, data.table, here, patchwork, conflicted)
conflict_prefer_all("dplyr", quiet = TRUE)

walk(c("fun_alm","fun_model", "Display_Functions"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
ds <- readRDS(here::here("data/e1_md_11-06-23.rds"))  |> as.data.table()
ids <- c(1,2,4,5,6,7,8, 10,11,12,13)
ids2 <- c(1,66,141,142,36,57,81)
ids3 <- c(20,71,101,4,76,192)

@@

```{r fig.width=11, fig.height=10}
ind_fits <- readRDS("~/Library/CloudStorage/GoogleDrive-tegorman13@gmail.com/My Drive/HTW/gl/data/indv_sim/ind_abc_ss_1000_ng100_bufp55.rds")
ind_fits <- ind_fits |> list_assign(runInfo = zap())

>>>>

walk(c("Display_Functions"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
ds <- readRDS(here::here("data/e1_md_11-06-23.rds"))  |> as.data.table()
ids <- c(1,2,4,5,6,7,8, 10,11,12,13)
ids2 <- c(1,66,141,142,36,57,81)
ids3 <- c(20,71,101,4,76,192)

source(here::here("Functions/fun_indv_fit.R"))

@@

```{r fig.width=11, fig.height=10}

ind_fits <- here::here(readRDS("data/ind_abc_ss_1000_ng100_bufp55"))
ind_fits <- ind_fits |> list_assign(runInfo = zap())
